**Supplementary Information**

### 2020-05-28 submission/supplementary.Rmd
First review.

```{r out.width="85%", fig.align="center", fig.cap="Rarefaction curves of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{C. nodosa} [Mixed Settlement] and \\textit{C. cylindracea} [Mixed and Monospecific Settlement]) and in the ambient seawater.\\label{rarefaction}", fig.pos="H"}
include_graphics("../results/figures/rarefaction.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{C. nodosa} [Mixed Settlement] and \\textit{C. cylindracea} [Mixed and Monospecific Settlement]) and in the ambient seawater.\\label{calculators}", fig.pos="H"}
include_graphics("../results/figures/calculators.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Relative contribution of chloroplast sequences on the surfaces of macrophytes (\\textit{C. nodosa} [Mixed Settlement] and \\textit{C. cylindracea} [Mixed and Monospecific Settlement]) and in the ambient seawater.\\label{chloroplast}", fig.pos="H"}
include_graphics("../results/figures/chloroplast_bar_plot.jpg")
```

@@

# Joining metadata with the number of sequences and OTUs
invisible(Sys.setlocale(locale="en_GB.utf8"))
metadata_nseq_notus <- inner_join(metadata, nseq_notus, by=c("ID"="Group")) %>%
  select(ID, station, date, season, nseq, notus) %>%
  mutate(date=as.Date(date, "%d.%m.%Y")) %>%
  mutate(date=format(date, "%d %B %Y")) %>%
  mutate(date=str_replace(date, "^0", "")) %>%
  arrange(match(station, c("F", "FCyM", "FCaM", "FCa"))) %>%
  mutate(station=str_replace(station, "^F$", "Seawater")) %>%
  mutate(station=str_replace(station, "^FCyM$", "\\\\textit{Cymodocea nodosa} (Mixed)")) %>%
  mutate(station=str_replace(station, "^FCaM$", "\\\\textit{Caulerpa cylindracea} (Mixed)")) %>%
  mutate(station=str_replace(station, "^FCa$", "\\\\textit{Caulerpa cylindracea} (Monospecific)")) %>%
  mutate(ID=str_replace(ID, "^23_1$", "23a")) %>%
  mutate(ID=str_replace(ID, "^23_2$", "23b")) %>%
  mutate(nseq=format(nseq, big.mark=","), notus=format(notus, big.mark=","))

# Generating the table
kable(metadata_nseq_notus, format="latex", booktabs=TRUE, linesep="", longtable=TRUE, escape=FALSE, col.names=c("Sample ID", "Community Type", "Date", "Season", "No. of Sequences", "No. of OTUs"), caption="Sample ID, Community Type, Sampling Date and Season, No. of Sequences and No. of OTUs of each sample. No. of Sequences and OTUs was calculated after the exclusion of eukaryotic, chloroplast, mitochondrial and no relative sequences.\\label{nseq_notus}", align="c") %>%
  kable_styling(latex_options=c("hold_position", "repeat_header"), font_size=9) %>%
  row_spec(0, bold=TRUE) %>%
  column_spec(1, width="6em")
```

>>>>

```{r out.width="85%", fig.align="center", fig.cap="Rarefaction curves of bacterial and archaeal communities from the surfaces of the macrophytes \\textit{C. nodosa} (Mixed Settlement) and \\textit{C. cylindracea} (Mixed and Monospecific Settlement) and in the ambient seawater.\\label{rarefaction}", fig.pos="H"}
include_graphics("../results/figures/rarefaction.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of the macrophytes \\textit{C. nodosa} (Mixed Settlement) and \\textit{C. cylindracea} (Mixed and Monospecific Settlement) and in the ambient seawater.\\label{calculators}", fig.pos="H"}
include_graphics("../results/figures/calculators.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Relative contribution of chloroplast sequences on the surfaces of the macrophytes \\textit{C. nodosa} (Mixed Settlement) and \\textit{C. cylindracea} (Mixed and Monospecific Settlement) and in the ambient seawater.\\label{chloroplast}", fig.pos="H"}
include_graphics("../results/figures/chloroplast_bar_plot.jpg")
```

@@

# Joining metadata with the number of sequences and OTUs
invisible(Sys.setlocale(locale="en_GB.utf8"))
metadata_nseq_notus <- inner_join(metadata, nseq_notus, by=c("ID"="Group")) %>%
  select(ID, station, date, season, nseq, notus) %>%
  mutate(date=as.Date(date, "%d.%m.%Y")) %>%
  mutate(date=format(date, "%d %B %Y")) %>%
  mutate(date=str_replace(date, "^0", "")) %>%
  arrange(match(station, c("F", "FCyM", "FCaM", "FCa"))) %>%
  mutate(station=str_replace(station, "^F$", "Seawater")) %>%
  mutate(station=str_replace(station, "^FCyM$", "\\\\textit{Cymodocea nodosa} (Mixed)")) %>%
  mutate(station=str_replace(station, "^FCaM$", "\\\\textit{Caulerpa cylindracea} (Mixed)")) %>%
  mutate(station=str_replace(station, "^FCa$", "\\\\textit{Caulerpa cylindracea} (Monospecific)")) %>%
  mutate(season=str_replace(season, "^Summer$", "summer")) %>%
  mutate(season=str_replace(season, "^Autumn$", "autumn")) %>%
  mutate(season=str_replace(season, "^Winter$", "winter")) %>%
  mutate(season=str_replace(season, "^Spring$", "spring")) %>%
  mutate(ID=str_replace(ID, "^23_1$", "23a")) %>%
  mutate(ID=str_replace(ID, "^23_2$", "23b")) %>%
  mutate(nseq=format(nseq, big.mark=","), notus=format(notus, big.mark=","))

# Generating the table
kable(metadata_nseq_notus, format="latex", booktabs=TRUE, linesep="", longtable=TRUE, escape=FALSE, col.names=c("Sample ID", "Community Type", "Date", "Season", "No. of Sequences", "No. of OTUs"), caption="Sample ID, Community Type, Sampling Date and Season, No. of Sequences and No. of OTUs of each sample. The number of sequences and OTUs was calculated after exclusion of sequences without known relatives (no relative sequences) and eukaryotic, chloroplast and mitochondrial sequences.\\label{nseq_notus}", align="c") %>%
  kable_styling(latex_options=c("hold_position", "repeat_header"), font_size=9) %>%
  row_spec(0, bold=TRUE) %>%
  column_spec(1, width="6em")
```
